---
title: "Lab 00 - Hello IDS!"
author: "JialinLiu"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter", "David", "Tony", 
           "Ben", "steven"),
  github_username = c("mcgregors-garden", "David4", "Tony2", 
                      "Ben3", "Steven4"), 
  colour = c("blue", "red", "yellow", 
             "green", "blue"),
  hobby = c("Hopping", "basketball", "football", 
            "football", "tennis"),
  favourite_number = c(2, 4, 5, 5, 9)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```
answer for exercise 18:plot shows a graph with github_username on x axes and favourite_number in axes, each block were filled with their favourite color. 

*Remove this text (including the stars), and add your answer for Exercise 18 here.*

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "hobby", 
          y = "github_username",
          title = "name")
```
answer for exercise 19: I think labs() here means making changes, like P1+labs(……）means it stil keep the feature of the first graph but it changes x asex to "hobby" and changes y asex to"github_username" and added a title for the plot since colour remains unchanged so it's still the same colour comparing with plot 1


*Remove this text (including the stars), and add your answer for Exercise 19 here.*

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*

answer for exercise 20: If every person got a different hobby then the plot will looks like the same height no useful conculsion can be made through the plot.

